The Impact of Immutability on Class Size

### 2020-04-06 paper1/article.tex
more

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\bibliographystyle{plainurl}
\title{The Impact of Class Immutability on NCSS}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\Moscow, Russia\\yegor.bugayenko@huawei.com}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{../total}
\begin{document}
\raggedbottom
\maketitle

\begin{abstract}
...
\end{abstract}

@@

A list of Java repositories were retrieved from GitHub via their
public API. The first \totalrepos{} repositories were taken, which satisfied
the selection criteria:
\begin{enumerate*}[label={\arabic*)}]
\item more than 1000 stars,
\item more than 200 Kb of data,
\item not archived,
\item public.
\end{enumerate*}
The list included popular Java open source products, like
Spring Framework, RxJava, Google Guava, and others.

>>>>

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\bibliographystyle{plainurl}
\title{The Impact of Immutability on Class Size}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\Moscow, Russia\\\texttt{yegor.bugayenko@huawei.com}}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{../total}
\begin{document}
\raggedbottom
\maketitle

\begin{abstract}
To be written later...
\end{abstract}

@@

A list of Java repositories were retrieved from GitHub via their
public API. The first \totalrepos{} repositories were taken, which satisfied
the selection criteria:
\begin{enumerate*}[label={\arabic*)}]
\item more than 1000 stars,
\item more than 200 Kb of data,
\item not archived,
\item public.
\end{enumerate*}
The list included popular Java open source products, like
Spring, RxJava, Guava, MyBatis, Clojure, JUnit, Lombok,
Graal, Selenium, Spark, Mockito, Jenkins, Netty, and others.
